### 2019-04-26 Bucketing/background.tex
Use less-confusing "bucketing problem" rather than "clustering problem"

We will follow the tradition of prior practitioners and use an existing
corpus of theorems as a \emph{ground truth} against which to compare results.
Prior work has used libraries of the \textsc{Isabelle/HOL} proof assistant as a
ground
truth~\cite{Montano-Rivas.McCasland.Dixon.ea:2012,johansson2009isacosy,claessen2013automating},
but these only contained a few definitions and theorems each. To analyse
behaviour on a larger scale, as required to study the effects of clustering, we
have chosen the \emph{Tons of Inductive Problems} (TIP) problem set for
automated theorem provers~\cite{claessen2015tip}.  Reasons for choosing TIP
include:

@@

\subsection{The Clustering Problem}
\label{sec:clustering}

% TODO{2019-04-18}

>>>>

We will follow the tradition of prior practitioners and use an existing
corpus of theorems as a \emph{ground truth} against which to compare results.
Prior work has used libraries of the \textsc{Isabelle/HOL} proof assistant as a
ground
truth~\cite{Montano-Rivas.McCasland.Dixon.ea:2012,johansson2009isacosy,claessen2013automating},
but these only contained a few definitions and theorems each. To analyse
behaviour on a larger scale, as required to study the effects of bucketing, we
have chosen the \emph{Tons of Inductive Problems} (TIP) problem set for
automated theorem provers~\cite{claessen2015tip}.  Reasons for choosing TIP
include:

@@

\subsection{The Bucketing Problem}
\label{sec:bucketing}

% TODO{2019-04-19}

### 2019-04-26 Bucketing/intro.tex
Use less-confusing "bucketing problem" rather than "clustering problem"

We dub such selection the \emph{clustering problem} for theory exploration and
analyse its effect on the running time of theory exploration tools on a
particular problem set, and on the quality of the statements they are able to
generate. An automated solution to this clustering problem would accept a large
number of definitions and efficiently select sub-sets which are both small
enough to reasonably explore, whilst still enabling interesting properties to be
discovered.

@@

\begin{enumerate}
  \item Defining the \emph{clustering problem} for theory exploration.
  \item Statistical analysis of theory exploration performance on a large
    problem set, derived from existing theorem proving problem sets.
  \item Empirical analysis of the effect of clustering on the quantity of
    desirable properties attainable by theory exploration.
  \item Experimental application of unsupervised machine learning to the
    clustering problem.
  % \item A novel feature extraction method for transforming Haskell expressions
  %   into a form amenable to off-the-shelf learning algorithms.
  % \item An implementation of these feature extraction and theory exploration
  %   approaches.
  % \item A comparison of our methods with existing approaches, both for theory
  %   exploration in Haskell, and for machine learning in other languages.
\end{enumerate}

We describe theory exploration in more detail, as well as the \qspec{} tool we
use in our experiments, in \S~\ref{sec:theoryexploration}. We introduce the
clustering problem more formally in \S~\ref{sec:clustering} and measure its
effect on theory exploration systems in \S~\ref{sec:implementation}. We attempt
(unsuccessfully) to apply machine learning to the clustering problem in
\S~\ref{sec:clustering}.  A variety of related work is surveyed in
\S~\ref{sec:related} and we conclude in \S~\ref{sec:conclusion} with potential
directions for future research.

>>>>

We dub such selection the \emph{bucketing problem} for theory exploration and
analyse its effect on the running time of theory exploration tools on a
particular problem set, and on the quality of the statements they are able to
generate. An automated solution to this bucketing problem would accept a large
number of definitions and efficiently select sub-sets which are both small
enough to reasonably explore, whilst still enabling interesting properties to be
discovered.

@@

\begin{enumerate}
  \item Defining the \emph{bucketing problem} for theory exploration.
  \item Statistical analysis of theory exploration performance on a large
    problem set, derived from existing theorem proving problem sets.
  \item Empirical analysis of the effect of bucketing on the quantity of
    desirable properties attainable by theory exploration.
  \item Experimental application of machine learning to the bucketing problem,
    via unsupervised \emph{clustering}.
  % \item A novel feature extraction method for transforming Haskell expressions
  %   into a form amenable to off-the-shelf learning algorithms.
  % \item An implementation of these feature extraction and theory exploration
  %   approaches.
  % \item A comparison of our methods with existing approaches, both for theory
  %   exploration in Haskell, and for machine learning in other languages.
\end{enumerate}

We describe theory exploration in more detail, as well as the \qspec{} tool we
use in our experiments, in \S~\ref{sec:theoryexploration}. We introduce the
bucketing problem more formally in \S~\ref{sec:bucketing} and measure its
effect on theory exploration systems in \S~\ref{sec:implementation}. In
\S~\ref{sec:clustering} we highlight the difference betwee bucketing and the
well-known \emph{clustering problem} from machine learning, by demonstrating
that clustering algorithms perform poorly at bucketing.  A variety of related
work is surveyed in \S~\ref{sec:related} and we conclude in
\S~\ref{sec:conclusion} with potential directions for future research.
